The Algorand Virtual Machine Specification

### 2021-02-28 tex/con.tex
Add support for equation conversion from tex to md
The equations will be converted using url images in the gfm directory and by html tags in the md directory.

Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

% Preamble
\documentclass{article}

% Packages
%\usepackage{amsmath}
%\usepackage{amssymb}

@@

    To mitigate this problem, for calculating a user's stake, instead of using the raw ALGO balance, we use the
    minimum of a \emph{trust value} that the system has calculated for the user and the user's ALGO balance:
    \[
        Stake_{user} = \min (Balance_{user},Trust_{user})
    \]
    For estimating the value of $Trust_{user}$ we use the exponential moving average of the user's ALGO balance.
    Therefore, in our system a user who held ALGOs and participated in the consensus for a long time is more trusted
    than a new user with a higher balance.
    An attacker who has obtained a large amount of ALGOs, also needs to hold them for a long period of time before
    being able to attack our system.

    For calculating the exponential moving average of a time series at the time step $t$, we can use the following
    recursive formula:
    \[
        M_{t} = (1 - \alpha) M_{t - 1} + \alpha X_{t} = M_{t - 1} + \alpha (X_{t} - M_{t - 1})
    \]
    Where:
    \begin{itemize}
        \item The coefficient $\alpha$ is a constant smoothing factor between 0 and 1 which represents the degree of
        weighting decrease, A higher $\alpha$ discounts older observations faster.
        \item $X_{t}$ is the value of the time series at the time step $t$.
        \item $M_{t}$ is the value of the EMA at the time step $t$.
    \end{itemize}

    Usually an account balance will not change in every time step, and we can use older values of EMA for calculating
    $M_{t}$:
    \[
        M_{t} = (1 - \alpha)^{t - k}M_{k} + [1 - (1 - \alpha)^{t - k}]X
    \]
    Where:
    \[
        X = X_{k+1} = X_{k+2} = \dots = X_t
    \]
    When $|nx| \ll 1$ we can use the binomial approximation  $(1 + x)^n \approx 1 + nx$ to further simplify this
    formula:
    \[
        M_{t} = M_{k} + (t - k) \alpha (X - M_{k})
    \]

    For choosing the value of $\alpha$ we can consider the number of time steps that the trust value of a user needs
    for reaching a specified fraction of his account balance.
    We know that for large $n$ and $|x| < 1$ we have $(1 + x)^{n} \approx e^{nx}$, so by letting $M_{k} = 0$ and
    $n = t - k$
    we can write:
    \[
        \alpha =- \frac{\ln\left(1 - \frac{M_{n + k}}{X}\right)}{n}
    \]
    The value of $\alpha$ for a desired configuration can be calculated by this equation.
    For instance, we could calculate the $\alpha$ for a relatively good configuration in which $M_{n+k} = 0.8X$ and $n$
    equals to the number of time steps of 10 years.
\end{document}

>>>>

% Preamble
\documentclass[11pt]{article}

% Packages
\usepackage{amssymb}
%\usepackage{amsmath}

@@

    To mitigate this problem, for calculating a user's stake, instead of using the raw ALGO balance, we use the
    minimum of a \emph{trust value} that the system has calculated for the user and the user's ALGO balance:
    \[
        Stake_{user} = \min (Balance_{user},Trust_{user})
    \]
    For estimating the value of \(Trust_{user}\) we use the exponential moving average of the user's ALGO balance.
    Therefore, in our system a user who held ALGOs and participated in the consensus for a long time is more trusted
    than a new user with a higher balance.
    An attacker who has obtained a large amount of ALGOs, also needs to hold them for a long period of time before
    being able to attack our system.

    For calculating the exponential moving average of a time series at the time step \(t\), we can use the following
    recursive formula:
    \[
        M_t = (1 - \alpha) M_{t-1} + \alpha X_t = M_{t-1} + \alpha (X_t - M_{t-1})
    \]
    Where:
    \begin{itemize}
        \item The coefficient \(\alpha\) is a constant smoothing factor between 0 and 1 which represents the degree of
        weighting decrease, A higher \(\alpha\) discounts older observations faster.
        \item \(X_t\) is the value of the time series at the time step \(t\).
        \item \(M_t\) is the value of the EMA at the time step \(t\).
    \end{itemize}

    Usually an account balance will not change in every time step, and we can use older values of EMA for calculating
    \(M_t\):
    \[
        M_t = (1 - \alpha)^{t-k}M_k + [1 - (1 - \alpha)^{t - k}]X
    \]
    Where:
    \[
        X = X_{k+1} = X_{k+2} = \dots = X_t
    \]
    When \(|nx| \ll 1\) we can use the binomial approximation  \((1 + x)^n \approx 1 + nx\) to further simplify this
    formula:
    \[
        M_t = M_k + (t - k) \alpha (X - M_k)
    \]

    For choosing the value of \(\alpha\) we can consider the number of time steps that the trust value of a user needs
    for reaching a specified fraction of his account balance.
    We know that for large \(n\) and \(|x| < 1\) we have \((1 + x)^n \approx e^{nx}\), so by letting \(M_k = 0\) and
    \(n = t - k\)
    we can write:
    \[
        \alpha =- \frac{\ln\left(1 - \frac{M_{n+k}}{X}\right)}{n}
    \]
    The value of \(\alpha\) for a desired configuration can be calculated by this equation.
    For instance, we could calculate the \(\alpha\) for a relatively good configuration in which \(M_{n+k} = 0.8X\)
    and \(n\) equals to the number of time steps of 10 years.
\end{document}
